\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-05 paper.tex
Explicit the knowledge dynamics management
Closes #4

In our architecture, knowledge manipulation relies on a central server (the {\sc
Oro} server~\cite{Lemaignan2010}, Figure~\ref{fig|spark-oro} top) which stores
knowledge as it is produced by each of the deliberative components. It
conversely exposes a {\tt json}-based RPC API~\cite{lemaignan2012kbapi} to query
the knowledge base.  We represent knowledge as RDF triples in the OWL
sub-language. Each time triples are added or removed from the knowledge base, a
Description Logics reasoner ({\sc Pellet}\footnote{\tt
http://clarkparsia.com/pellet/}) classifies the whole ontology and inserts all
possible inferred triples.

>>>>

In our architecture, knowledge manipulation relies on a central server (the {\sc
Oro} server~\cite{Lemaignan2010}, Figure~\ref{fig|spark-oro} top) which stores
knowledge as it is produced by each of the deliberative components (the
clients). It exposes a {\tt json}-based RPC API~\cite{lemaignan2012kbapi} to
query the knowledge base. The clients of the {\sc Oro} server are in charge of
managing themselves the knowledge (when to add, when to update, when to
retract knowledge): no meta-semantics is carried over that would let the server
manage these dynamics itself.\footnote{There is one exception: so-called
\emph{memory profiles} let the server discard facts after a specific period
of time. We present this experimental feature at section~\ref{memory}.} We
represent knowledge as RDF triples in the OWL sub-language. Each time
triples are added or removed from the knowledge base, a Description Logics
reasoner ({\sc Pellet}\footnote{\tt http://clarkparsia.com/pellet/})
classifies the whole ontology and inserts all possible inferred triples.
